A Method for the Spectroscopic Inference of Stellar Parameters

### 2014-06-29 tex/paper.tex
updated path

\documentclass[preprint]{aastex} 
%\documentclass[iop,floatfix]{emulateapj}

@@

\section{Methodology \label{sec:method}}

@@

\subsection{Post-Processing \label{subsec:postprocess}}

@@

\begin{figure*}[!htb]
\begin{center}
  \includegraphics{figs/kernels.pdf}
  \includegraphics{figs/high2low.pdf}
  \caption{Panel 1: the instrumental (${\rm FWHM} =6.8\;\kms$) and rotational ($v \sin i = 5\;\kms$) broadening kernels, and their composite. Panel 2: A section of the raw, high resolution synthetic model at $R=$500,000. Panel 3: The spectrum after applying the composite broadening kernel, $\varphi_v$. Panel 4: The broadened spectrum downsampled to the pixels of the detector.}
\label{fig:broadening}
\end{center}
\end{figure*}

% SA: My idea for this figure is sort of 1-column wide (~3.5"), with a set of spectral panels going 
% down vertically.  The top panel shows a segment of the full resolution model.  The next one down 
% can show the individual kernels described above, as well as their composite, \varphi_v.  Then the 
% next panel down can show the convolved (but still full-resolution) spectrum.  Finally, the bottom 
% panel will show the spectrum re-sampled onto the observed pixels.  It need not be a large figure 
% (maybe 5" long?).

@@

We adopt a somewhat analogous approach to deal with this issue, but cast it internal to the 
modeling framework to appropriately propagate the uncertainty introduced by additional degrees of 
freedom in the model.  The residual calibration errors are treated as an explicit contribution to 
the model spectrum, enabling us to explore the distribution of possible calibrations (see 
Section~\ref{subsec:MCMC}) and then eventually marginalize out the associated nuisance parameters.  
In essence, the inferences for the relevant stellar parameters will properly account for the 
underlying uncertainty in the calibration process.  This is achieved in practice by distorting the 
model spectrum with a (low-order) Chebyshev polynomial \citep[e.g.,][]{eisenstein06,koleva09}, 
\begin{equation}
\vM(\vt, \vT_{\rm cheb}) = \vM(\vt) \times \sum_n c_n \, T_n,
\end{equation}
where $T_n$ are the standard Chebyshev functions of order $n$ and the coefficients are treated as a
set of nuisance (hyper-)parameters, $\vT_{\rm cheb} = \{c_n\}^{\rm order}$, for each available 
spectral order in the dataset.  With judicious priors on $\vT_{\rm cheb}$, we can ensure that the 
unintended treatment of real spectral features (e.g., broad, deep molecular bands) as calibration 
artifacts is negligible (see Secton~\ref{sec:examples} for examples).  The lowest-order (scaling) 
coefficient, $c_0$, is by its nature degenerate with the solid angle parameter, $\Omega$.  
Therefore, we enforce an additional constraint by requiring that the mean of the polynomial is 
unity.  For data with a single spectral order, this means setting $c_0 = 1$.  If the goal is to 
model multiple spectral orders, we assign $c_0 = 1$ in an arbitrary order as an anchor, but permit 
the $c_0$ values in other orders to be different (as necessary).  It is worth noting that this 
formalism can, in principle, be extended to develop models for completely uncalibrated spectra, 
rather than the residual calibration mismatches as described here (with a suitable relaxation of 
the priors on $\vT_{\rm cheb}$).  Figure \ref{fig:cheb} offers a practical demonstration of how 
these nuisance parameters are applied. 
\comm{I envision this figure much like the previous one, in a 1-column vertical distribution of 
 panels.  At top, you would show the data spectrum at an overlap of two spectral orders, along 
 with the post-processed model with no Chebyshev polynomials applied.  Next, you would show the 
 two Chebyshev polynomials appropriate for the two orders.  And then in the final panel you would 
 revisit the top panel with the polynomials applied, demonstrating the improvement.}

\subsection{Model Evaluation \label{subsec:likelihood}}

@@

\comm{No idea if this is your intention for $b$, but it was the only way I could rationalize it.}

@@

\subsection{Exploring the Posterior \label{subsec:MCMC}}

>>>>

%\documentclass[preprint]{aastex} 
\documentclass[iop,floatfix]{emulateapj}

@@

\section{Methodology} \label{sec:method}

@@

\subsection{Post-Processing}
\label{subsec:postprocess}

@@

\begin{figure}[!htb]
\begin{center}
  \includegraphics{figs/kernels.pdf}
  \includegraphics{figs/high2low.pdf}
  \caption{Panel 1: the instrumental (${\rm FWHM} =6.8\;\kms$) and rotational ($v \sin i = 5\;\kms$) broadening kernels, and their composite. Panel 2: A section of the raw, high resolution synthetic model at $R=$500,000. Panel 3: The spectrum after applying the composite broadening kernel, $\varphi_v$. Panel 4: The broadened spectrum downsampled to the pixels of the detector.}
\label{fig:broadening}
\end{center}
\end{figure}

@@

We adopt a somewhat analogous approach to deal with this issue, but cast it internal to the 
modeling framework to appropriately propagate the uncertainty introduced by additional degrees of 
freedom in the model.  The residual calibration errors are treated as an explicit contribution to 
the model spectrum, enabling us to explore the distribution of possible calibrations (see 
Section~\ref{subsec:MCMC}) and then eventually marginalize out the associated nuisance parameters.  
In essence, the inferences for the relevant stellar parameters will properly account for the 
underlying uncertainty in the calibration process.  This is achieved in practice by distorting the 
model spectrum with a (low-order) Chebyshev polynomial \citep[e.g.,][]{eisenstein06,koleva09}, 
\begin{equation}
\vM(\vt, \vT_{\rm cheb}) = \vM(\vt) \times \sum_n c_n \, T_n,
\end{equation}
where $T_n$ are the standard Chebyshev functions of order $n$ and the coefficients are treated as a
set of nuisance (hyper-)parameters, $\vT_{\rm cheb} = \{c_n\}^{\rm order}$, for each available 
spectral order in the dataset.  With judicious priors on $\vT_{\rm cheb}$, we can ensure that the 
unintended treatment of real spectral features (e.g., broad, deep molecular bands) as calibration 
artifacts is negligible (see Secton~\ref{sec:examples} for examples).  The lowest-order (scaling) 
coefficient, $c_0$, is by its nature degenerate with the solid angle parameter, $\Omega$.  
Therefore, we enforce an additional constraint by requiring that the mean of the polynomial is 
unity.  For data with a single spectral order, this means setting $c_0 = 1$.  If the goal is to 
model multiple spectral orders, we assign $c_0 = 1$ in an arbitrary order as an anchor, but permit 
the $c_0$ values in other orders to be different (as necessary).  It is worth noting that this 
formalism can, in principle, be extended to develop models for completely uncalibrated spectra, 
rather than the residual calibration mismatches as described here (with a suitable relaxation of 
the priors on $\vT_{\rm cheb}$).  Figure \ref{fig:chebyshev} offers a practical demonstration of how 
these nuisance parameters are applied.

\begin{figure}[!htb]
\begin{center}
  \includegraphics{figs/chebyshev.pdf}
  \caption{A region of the echelle spectrum at the overlap between two adjacent orders of the echelle spectrum. Panel 1: In green and blue, we have the flux-calibrated dataset. The adjacent orders overlap but there is a slight discrepancy of $\lesssim 3$\%. In the background in red is a model spectrum generated for reasonable values of stellar parameters, $\vt$. Panel 2: In order to account for residual errors in the flux calibration, we allow the model to be multiplied by a Chebyshev polynomial. Here are the polynomials determined as best fit, to multiply the model. Panels 3 \& 4: In principle, we could divide the data by these polynomials to recover what the true flux-calibrated data should be (panel 3), but instead we multiply the model by the polynomials to recover the original discrepancy between orders (panel 4). This has the advantage of preserving the original dataset as a fixed quantity and makes the model linear in the Chebyshev polynomial coefficients.}
\label{fig:chebyshev}
\end{center}
\end{figure}

\subsection{Model Evaluation}
\label{subsec:likelihood}

@@

@@

\subsection{Exploring the Posterior }
\label{subsec:MCMC}
